%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\begin{cventries}
  \cventry
    {Graduate Research Assistant - Department of Geography}
    {Oklahoma State University}
    {Stillwater, Oklahoma}
    {Jan. 2016 - Present}
    {
      \begin{expitems}
        \item {Diagnosed and fixed issues in Microsoft SQL Server databases}
        \item {Wrote programs in C\#, designed web pages in the Microsoft .NET framework}
        \item {Improved the functionality, security, and aesthetics of
            Oklahoma's State Historic Preservation websites}
      \end{expitems}
    }

  \cventry
    {Graduate Teaching Assistant - Department of Geography}
    {}
    {}
    {Aug. 2012 - Dec. 2015}
    {
      \begin{expitems}
      \item {Taught \textit{Introduction to Cultural Geography} (lecture) for three
          semesters}
      \item {Taught \textit{Introduction to Physical Geography} (lecture) for one
          semester}
      \item {Taught \textit{Introduction to Physical Geography} (laboratory) for five
          semesters}
      \end{expitems}
    }

  \cventry
    {Programmer - Department of Plant and Soil Sciences}
    {}
    {}
    {May 2015 - Aug. 2015}
    {
      \begin{expitems}
      \item {Worked with a research team to develop an automated soil moisture
          mapping system}
        \item {Led a workshop session on soil moisture mapping using the MATLAB
            Mapping Toolbox}
        \item {Helped develop a MATLAB kriging library}
      \end{expitems}
    }

  \cventry
    {Transportation Intern}
    {Association of Central Oklahoma Governments}
    {Oklahoma City, Oklahoma}
    {May 2013 - Aug. 2013}
    {
      \begin{expitems}
        \item {Conducted spatial analysis using ArcGIS}
        \item {Wrote vast formulas in Microsoft Excel to organize data for over 125,000 car crashes}
        \item {Updated land use shapefiles in a network geodatabase}
      \end{expitems}
    }

  \cventry
    {CAVE Instructor}
    {Neosho County Community College}
    {Pittsburg, Kansas}
    {Aug. 2011 - Dec. 2011}
    {
      \begin{expitems}
        \item {Taught \textit{Intermediate Algebra} to 22 incoming freshmen}
        \item {Designed all class assignments, delivered all lectures, wrote and
            proctored all exams}
      \end{expitems}
    }
    
  \cventry
    {Student Teacher}
    {St. Mary's Colgan High School}
    {Pittsburg, Kansas}
    {Jan. 2011 - May. 2011}
    {
      \begin{expitems}
      \item {Taught two sections of \textit{Algebra II} and two sections of
          \textit{Geometry}}
        \item {Substitute taught in \textit{Calculus}, \textit{Algebra III}, and
            Junior High \textit{Physical Education}}
      \end{expitems}
    }

  \cventry
    {Mathematics Tutor - Mathematics Department}
    {Pittsburg State University}
    {Pittsburg, Kansas}
    {Jan. 2009 - May 2011}
    {
      \begin{expitems}
      \item {Tutored students in \textit{Calculus I}, \textit{Calculus II},
          \textit{Calculus III}, \textit{Discrete Mathematics}, \textit{Abstract
            Algebra}, \textit{Mathematical Modeling}, \textit{Probability and
            Statistics}, \textit{Elementary Statistics}, and \textit{College
            Algebra}}
      \end{expitems}
    }
\end{cventries}