\cvsection{Invited Lectures}
\begin{cventries}

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {Maintaining graduate student life. In \textit{GEOG-5001 -
              Professional Development in Geography.} Oklahoma State University.
            November \textbf{2017}, November \textbf{2016}.}
          \end{cvitems}
        } % there must be an empty space below or else items will be improperly indented

  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \vspace{-3mm}
      \item {Big data, spatial data science, and volunteered geographic
          information. In \textit{GEOG-2344 - Digital Tools for Environmental
            Exploration.} Oklahoma State University. September \textbf{2017}}.
        \end{cvitems}
    }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
         \vspace{-3mm}
       \item {High performance computing in the social sciences. In
           \textit{MATH-2910 - High Performance Computing.} Oklahoma State
           University. March \textbf{2016}.}
          \end{cvitems}
        } % there must be an empty space below or else items will be improperly indented
          
  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {The emergence of urban segregation in the United States. In
            \textit{GEOG-1113 - Introduction to Cultural Geography.} Oklahoma
            State University. March \textbf{2016}.}
          \end{cvitems}
        } % there must be an empty space below or else items will be improperly indented

  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \vspace{-3mm}
      \item {GIS programming with PostgreSQL and PostGIS. In \textit{GEOG-4383 -
            Introduction to GIS Programming.} Oklahoma State University. March
          \textbf{2016}.}
            \end{cvitems}
        } % there must be an empty space below or else items will be improperly indented

  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \vspace{-3mm}
      \item Volunteered geographic information, Twitter, and big data. In
        {\textit{GEOG-2344 - Digital Tools for Environmental Exploration.}
          Oklahoma State University. January \textbf{2016}, November
          \textbf{2015}}.
        \end{cvitems}
    }

\end{cventries}