\cvsection{Professional \& University Service}
\begin{cventries}
  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{Alternate Member}. \textit{OSU Student University
              Technology Services Fee Committee (UTSF)}. Oklahoma State
            University. November \textbf{2017} - present.}
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{Secretary}. \textit{Gamma Theta Upsilon (Geography Honor
              Society)}. Oklahoma State University. August \textbf{2017} -
            present.}
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{President}. \textit{Forum of Geography Graduate
              Students}. Oklahoma State University. August \textbf{2016} -
            February \textbf{2018}.} 
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{Co-organizer}. \textit{Forum of Geography Graduate
              Students invited colloquium presentations}. Stillwater, Oklahoma.
            Department of Geography Colloquia. August \textbf{2016} - present.}
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{Co-organizer}. \textit{Open source software in geography:
              Theories, developments, and pathways toward openness}. AAG Annual
            Meeting. Boston, Massachusetts. Paper Session. April \textbf{2017}.}
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{Co-organizer}. \textit{Open source software in geography:
              Theories, developments, and pathways toward openness}. AAG Annual
            Meeting. Boston, Massachusetts. Panel Session. April \textbf{2017}.}
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{Co-organizer}. \textit{Securing positions in academia}.
            Forum of Geography Graduate Students Special Sessions. Stillwater,
            Oklahoma. Three Part Lecture Series. January \textbf{2017}.}
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{President}. \textit{OSU Fellowship of Christian Graduate
              Students}. Oklahoma State University. August \textbf{2013} -
            May \textbf{2015}.} 
          \end{cvitems}
          }

  \cventry
    {}
    {}
    {}
    {}
    {
       \begin{cvitems}
          \vspace{-3mm}
        \item {\textbf{Treasurer}. \textit{Forum of Geography Graduate
              Students}. Oklahoma State University. August \textbf{2012} - July
            \textbf{2013}. }
          \end{cvitems}
          }
\end{cventries}