%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\begin{cventries}
  \cventry
    {Graduate Research Assistant - Department of Geography}
    {Oklahoma State University}
    {Stillwater, Oklahoma}
    {Jan. 2016 - Present}
    {
      \begin{cvitems}
        \item {Diagnosed and fixed issues in Microsoft SQL Server databases}
        \item {Improved the functionality, security, and aesthetics of Oklahoma's State Historic Preservation website}
        \item {Wrote programs in C\#, designed web pages in the Microsoft .NET framework}
      \end{cvitems}
    }

  \cventry
    {Graduate Teaching Assistant - Department of Geography}
    {}
    {}
    {Aug. 2012 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Taught Intro. to Cultural Geography (lecture) for three semesters}
        \item {Taught Intro. to Physical Geography (lecture) for one semester}
        \item {Taught Intro. to Physical Geography (laboratory) for five semesters}
      \end{cvitems}
    }

  \cventry
    {Programmer - Department of Plant and Soil Sciences}
    {}
    {}
    {May 2015 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Led a workshop session on soil moisture mapping using the MATLAB Mapping Toolbox}
        \item {Helped develop an automated soil moisture mapping system}
        \item {Aided in developing a MATLAB kriging library}
      \end{cvitems}
    }

  \cventry
    {Transportation Intern}
    {Association of Central Oklahoma Governments}
    {Oklahoma City, Oklahoma}
    {May 2013 - Aug. 2013}
    {
      \begin{cvitems}
        \item {Conducted spatial analysis using ArcGIS}
        \item {Wrote vast formulas in Microsoft Excel to organize data for over 125,000 car crashes}
        \item {Updated land use shapefiles in a network geodatabase}
      \end{cvitems}
    }

  \cventry
    {CAVE Instructor}
    {Neosho County Community College}
    {Pittsburg, Kansas}
    {Aug. 2011 - Dec. 2011}
    {
      \begin{cvitems}
        \item {Taught \textit{Intermediate Algebra} to incoming freshmen}
        \item {Was the sole instructor in a class of 22 students}
      \end{cvitems}
    }
    
  \cventry
    {Student Teacher}
    {St. Mary's Colgan High School}
    {Pittsburg, Kansas}
    {Jan. 2011 - May. 2011}
    {
      \begin{cvitems}
        \item {Taught two sections of \textit{Algebra II} and two sections of \textit{Geometry}}
        \item {Substitute taught in \textit{Calculus}, \textit{Algebra III}, and Junior High \textit{Physical Education}}
      \end{cvitems}
    }

  \cventry
    {Mathematics Tutor - Mathematics Department}
    {Pittsburg State University}
    {Pittsburg, Kansas}
    {Jan. 2009 - May 2011}
    {
      \begin{cvitems}
        \item {Tutored students in Calculus I, Calculus II, Calculus III, Discrete Mathematics, Abstract Algebra, \\ Mathematical Modeling, Probability and Statistics, Elementary Statistics, and College Algebra}
      \end{cvitems}
    }
\end{cventries}