\cvsection{Professional Conference Presentations}
\begin{cventries}
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
            \item {\textbf{Haffner, M.*}, A. Mathews., E. Ellis.
                \textit{GIS-based modeling of tornado siren sound propagation in
                  Stillwater, Oklahoma}. Southwest AAG Annual Meeting. Denton,
                TX. Poster  presentation. November \textbf{2016}.}
            \end{cvitems}
          }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
        \item {\textbf{Haffner, M.*}, A. Mathews. \textit{A multi-dimensional topology for crowd-sourced geographic information}. NSF Workshop on Geospatial Data Science in the Era of Big Data and CyberGIS. Urbana, Illinois. Paper presentation. July \textbf{2016}.} 
          \end{cvitems}
              }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
        \item A. Finchum*, {\textbf{M. Haffner}, A. Mathews, E. Fekete. \textit{Analyzing Smartphone Usage Patterns at Colleges with Strong Gender Differences Using Social Media}. Association of American Geographers Annual Meeting. San Franciso, California. Poster presentation. April \textbf{2016}.} 
            \end{cvitems}
            }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
            \item {\textbf{Haffner, M.*} \textit{Conquering big spatial data: Towards a new philosophy in geographic information science}. Oklahoma State University Research Symposium. Poster presentation. February \textbf{2016}.}   
              \end{cvitems}
            }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
            \item {Ochsner, T.* E., J. Dong, \textbf{M. Haffner}, A. Patrignani, J. C. Patton. \textit{Developing an operational system for daily 800-m resolution soil moisture estimates across Oklahoma}. American Geophysical Union Fall Meeting. San Francisco, California. Paper presentation. December \textbf{2015}.} 
            \end{cvitems}
            }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
            \item {\textbf{Haffner, M.*}, H. Yu. \textit{Measuring social interaction potential in Oklahoma City and Tulsa}. Association of American Geographers Annual Meeting. Chicago, Illinois. Paper Presentation. April \textbf{2015.}} 
              \end{cvitems}
              }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
            \item {Finchum, G. A.*, \textbf{M. Haffner}. \textit{Using Twitter data to analyze mobile device usage patterns in urban areas}. Association of American Geographers Annual Meeting. Chicago, Illinois. April \textbf{2015}.}  
              \end{cvitems}
            }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
            \item {\textbf{Haffner, M.*} \textit{Using ArcGIS, Python, and R to measure social interaction potential in Tulsa and Oklahoma City}. Technical presentation. Oklahoma South Central Arc User Group Meeting. Moore, Oklahoma. September \textbf{2014}.} 
            \end{cvitems}
            }
   \cventry
      {}
      {}
      {}
      {}
      {
        \begin{cvitems}
          \vspace{-2mm}
            \item {\textbf{Haffner, M.*} \textit{Measuring social interaction potential in Tulsa and Oklahoma City: A case study}. Oklahoma State University Research Symposium. Paper presentation. Stillwater, Oklahoma. April \textbf{2014}.} \\\\
            \textit{* Notes presenting author}
              \end{cvitems}
            }
\end{cventries}